Main text : Effect of copula on extinction risk

### 2019-02-27 MainText.Rmd
several changes, Table added

<!--FIG :  summary : all nonlinear model results for local dispersion : extrisk vs. d-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=15 cm]{./Results/allmodel_ext_risk_local_disp.pdf}
\caption{For each of six nonlinear density-dependence models presented in Table \ref{tab_model_info} extinction risk varies as dispersion-rate ($d$) goes from $0$ to $0.5$ for local dispersion. Last two columns represent extinction risk calculated for bifurcation parameter $(r)$ taken from under-compensatory and over-compensatory regime in deterministic model analog.\label{fig_extrisk_allmodel_localdisp}}
\end{center}
\end{figure}

@@

>>>>

<!--FIG :  summary : all nonlinear model results for local dispersion : extrisk vs. d-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=15 cm]{./Results/allmodel_ext_risk_local_disp.pdf}
\caption{For each of six nonlinear density-dependence models presented in Table \ref{tab_model_summary}, extinction risk varies as dispersion-rate ($d$) goes from $0$ to $0.5$ for local dispersal. Last two columns represent extinction risk calculated for bifurcation parameter $(r)$ taken from under-compensatory and over-compensatory regime of deterministic model analog.\label{fig_extrisk_allmodel_localdisp}}
\end{center}
\end{figure}

@@

```{r read_tab_model_summary,echo=F, results='asis',message=F}
library(kableExtra)
library(dplyr)
dt<-readRDS("./Results/tab_model_summary.RDS")
knitr::kable(dt, escape=F,
             format="latex",digits=4, align="l",
             caption = "Summary of models.\\label{tab_model_summary}",
             booktabs=T, linesep = "\\addlinespace"
             )%>%column_spec(c(1,3,5,6),width="1.4cm")%>%kable_styling(latex_options = "basic",position = "center")
             #column_spec(1, width = "8.5cm")%>%kable_styling(latex_options = "basic",position = "center")
```
